---
title: "Istanbul, Türkiye"
---

The Second Rome.

```{r out.width='100%', echo=FALSE}
hagiaSophia <- paste("<b>Hagia Sophia</b>")
topkapiPalace <- paste("<b>Topkapi Palace</b>")
istanbulArchaeologicalMuseum <- paste("<b>Istanbul Archaeological Museum</b>")
suleymaniye <- paste("<b>Süleymaniye Mosque</b>")
camlica <- paste("<b>Çamlıca Mosque</b>")
columnOfConstantine <- paste("<b>Column of Constantine</b>")
galataTower <- paste("<b>Galata Tower</b>")
grandBazaar <- paste("<b>Grand Bazaar</b>")
theodosianWalls <- paste("<b>Theodosian Walls</b>")
blueMosque <- paste("<b>Blue Mosque</b>")
basilicaCistern <- paste("<b>Basilica Cistern</b>")
maidensTower <- paste("<b>Maiden's Tower</b>")
princesIslands <- paste("<b>Princes' Islands</b>")
```
library(leaflet)
leaflet() %>% addTiles() %>%
  setView(2.346940, 48.858885, zoom = 13) %>%
  addMarkers(1.441974, 43.608382, icon = greenDotIcon, popup = eiffelTower) %>% # Eiffel Tower
  addMarkers(1.439878, 43.603737, icon = greenDotIcon, popup = arcDeTriomphe) %>% # Arc de Triophe
  addMarkers(1.490920, 43.586797, icon = greenDotIcon, popup = louvre) %>% # Louvre
  addMarkers(1.443809, 43.604417, icon = greenDotIcon, popup = sacreCoeur) %>% # Sacré Coeur
  addMarkers(1.443809, 43.604417, icon = greenDotIcon, popup = lesInvalides) %>% # Les Invalides
  addMarkers(1.443809, 43.604417, icon = greenDotIcon, popup = notreDame) %>% # Notre Dame
  addMarkers(1.490920, 43.586797, icon = greenDotIcon, popup = versailles) # Versailles
```



```{r echo = FALSE, results = 'asis'}
titles <- c("Length of Stay", "Transportation", "Major Sights","Unique Foods", "Restaurant Recommendations")
values <- c("Two months", "3 hour flight from Frankfurt", "Hagia Sophia, Topkapi Palace, Istanbul Archaeological Museum, Süleymaniye, Çamlıca", "Iskender kebab", "")
df <- data.frame(titles, values)
library(knitr)
kable(df, col.names = NULL)
```