---
title: "Split, Croatia"
---

When I'm a retired Emperor, I might decide to grow cabbages here too.

```{r out.width='100%', echo=FALSE}
diocletiansPalace <- paste("<b>Diocletian's Palace</b>")
archaeologicalMuseum <- paste("<b>Split Archaeological Museum</b>")
salona <- paste("<b>Salona</b>")
marjanHill <- paste("<b>Marjan Hill</b>")
library(leaflet)
leaflet() %>% addTiles() %>%
  setView(16.479874, 43.526796, zoom = 12) %>%
  addMarkers(16.438682, 43.508288, icon = greenDotIcon, popup = diocletiansPalace) %>% # Diocletian's Palace
  addMarkers(16.434599, 43.515919, icon = greenDotIcon, popup = archaeologicalMuseum) %>% # Split Archaeological Museum
  addMarkers(16.483451, 43.539609, icon = greenDotIcon, popup = salona) %>% # Salona
  addMarkers(16.413018, 43.511177, icon = greenDotIcon, popup = marjanHill) # Marjan Hill
```

```{r echo = FALSE, results = 'asis'}
titles <- c("Length of Stay", "Transportation", "Major Sights", "Restaurant Recommendations")
values <- c("4 days", "Flight from Lille, France", "Diocletian's Palace, Roman ruins of Solin", "Sladoledarnica Emiliana (possibly the best ice cream I've ever had)")
df <- data.frame(titles, values)
library(knitr)
kable(df, col.names = NULL)